\vspace{-2cm}A generative model for urban firm networks

### 2022-03-31 CoverLetter.tex

We have no conflicts of interest to disclose. We do not have any opposed reviewer. This paper is submitted to the PloS ONE collection ``Cities as Complex Systems'' edited by M. Gonzalez (University of California, Berkeley) and D. Rybski (Potsdam Institute for Climate Impact Research). We know that the official deadline has passed, nevertheless, we hope that it could still be considered for this special issue.

>>>>

We have no conflicts of interest to disclose. We do not have any opposed reviewer. This paper was initially submitted to the PloS ONE collection ``Cities as Complex Systems'' edited by M. Gonzalez (University of California, Berkeley) and D. Rybski (Potsdam Institute for Climate Impact Research). We know that the official deadline has passed, nevertheless, we hope that it could still be considered for a non-special issue.
